---
title: "Pokemon Characteristics and Classification"
output:
 html_document:
    theme: united
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Data Set:

Pokemon dataset contains information on a total of 802 Pokemon.

it includes:

* The English name of the Pokemon
* percentage_male: The percentage of the species that are male. Blank if the Pokemon is genderless.
* height_m: Height of the Pokemon in metres
* weight_kg: The Weight of the Pokemon in kilograms
* hp: The Base HP of the Pokemon
* attack: The Base Attack of the Pokemon
* defense: The Base Defense of the Pokemon
* speed: The Base Speed of the Pokemon
* base_egg_steps: The number of steps required to hatch an egg of the Pokemon
* base_happiness: Base Happiness of the Pokemon
* capture_rate: Capture Rate of the Pokemon
* experience_growth: The Experience Growth of the Pokemon
* sp_attack: The Base Special Attack of the Pokemon
* sp_defense: The Base Special Defense of the Pokemon
* type1: The Primary Type of the Pokemon
* generation: The numbered generation which the Pokemon was first introduced
* is_legendary: Denotes if the Pokemon is legendary.



Data Sources: https://www.kaggle.com/rounakbanik/pokemon/data


```{r cars}
D=read.csv('Pokemon.csv',header = T)
library(DT)
datatable(D, rownames = 1, filter="top", options = list(pageLength = 5, scrollX=T) )
summary(D)
```



